\section{Peer-reviewed Publications}
% AGU style: https://publications.agu.org/agu-grammar-and-style-guide/
\newcommand{\CS}{*} % corresponding author
\newcommand{\CF}{\textsuperscript{\#}} % co-first author

\CS corresponding author, \CF co-first author.
\begin{etaremune}
\item
    \Di, Xie, W., \& Xu, M. (2022).
    Seismic investigation of fine-scale upper crust structure along the northern East Pacific Rise.
    \textit{Chinese Journal of Geophysics}, \textit{Have been received}.
    \DOI{10.6038/cjg2022Q0006}.
\item
    Zhang, M., \Di\CF, Xu, M., Canales, C., Yu, C., Zhao, X., Wang, P., Zeng, X., \& Wang, Y. (2022).
    Seismic Imaging of Dante's Domes Oceanic Core Complex From Streamer Waveform Inversion and Reverse Time Migration.
    \textit{Journal of Geophysical Research: Solid Earth}, \textit{127}, e2021JB023814.
    \DOI{10.1029/2021JB023814}.
\item
    Zhang, M., Xu, M., Zhao, X., Zhang, J., Zha, C., Vithana, M., \Di, \& Zeng, X. (2020).
    Application of Kirchhoff downward-continued method to travel-time inversion of synthetic multi-channel seismic data.
    \textit{Journal of Tropical Oceanography}, \textit{39}(4), 80--90.
    \DOI{10.11978/2019087}.
\item
    Xu, M., \Di, Zhou, Z., Li, H., \& Lin, J. (2019).
    Interaction between hydrosphere and lithosphere in subduction zones.
    \textit{Marine Geology and Quaternary Geology}, \textit{39}(5), 58--70.
    \DOI{10.16562/j.cnki.0256-1492.2019063001}.
\item
    \Di, Deng, B., Zhao, G., Ye, Y., \& Qiu, J. (2018).
    The evolution of the river system on the Yunnan-Guizhou Plateau and formation process of the plateau based on modern river sediment.
    \textit{Acta Geologica Sichuan}, \textit{38}(4), 536--541.
    \DOI{10.3969/j.issn.1006-0995.2018.04.002}.
\end{etaremune}

\subsection*{Papers under Revision/Review}
\begin{etaremune}
    \item
    \Di, Xu, M., \& Xie, W.
    Upper crustal Vp/Vs ratios along the northern East Pacific Rise derived from downward-continued streamer data.
\item
    Xie, W., \Di, Zhang, M., \&  Xu, M.
    High-resolution seismic imaging of shallow structure near proposed IODP drilling sites, Kane Oceanic Core Complex, Mid-Atlantic Ridge.
\end{etaremune}

%\subsection*{Papers in Preparation}
%\begin{etaremune}
%\end{etaremune}
